Figures

### 2018-04-03 scripts/analysis.Rmd
better heatmap plot
additional expl. plot, improve table caption, adjust conny designation

```{r cor_mat_hmap, echo=FALSE, warning=FALSE, out.width="3.5in", fig.cap="Connectivity metric correlation heatmap.", message=FALSE}

@@

```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots cont"}

>>>>

```{r cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.2, fig.cap="Connectivity metric correlation heatmap.", message=FALSE}

@@

```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3.5, fig.cap="Exploratory plots cont"}
